Effects of epidemiological structure on the transient evolution of HIV virulence

### 2017-01-27 ms/cover_letter/plosHIVcover_resubm2.tex
update fig S4 caption, etc
work on cover letter

\response{

@@

\revcomment{
\textbf{Discussion:}
Would be helpful to start off by summarizing the main goals of the paper and then the main findings of the paper. Then, can get into limitations
}

\revcomment{
It would be very helpful to be able to give a intuitive or at least qualitative explanation for why these mixing patterns have such an influence on virulence.
}

@@

\response{

>>>>

\response{
We have thoroughly revised the captions.
}

\revcomment{
\textbf{Discussion:}
Would be helpful to start off by summarizing the main goals of the paper and then the main findings of the paper. Then, can get into limitations
}
\response{

@@

\revcomment{
It would be very helpful to be able to give a intuitive or at least qualitative explanation for why these mixing patterns have such an influence on virulence.
}
\response{

@@

\response{
We agree with the reviewers that this is a ``rather theoretical'' finding,
but we think it is important and useful nonetheless.  As we mention
in the discussion, the decision to examine the effects of contact
structure does not mean we can feel free to ignore all other aspects
of epidemiological realism; on the other hand, data for
parameterization and time for building and checking models is
limited, so we have to prioritize in some way. We would argue that
both quantifying the effects of contact structure and understanding
how they work is a useful, albeit incremental, step toward reliable
models of HIV eco-evolutionary dynamics.
}
